---
title: "Portland Crime Statistics 2004-2014"
author: "Peter Bates"
date: "April 18, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

	Over the past several decades, public awareness of crime has increased significantly. Those who do follow the news are exposed to a constant iteration of story after story about illegal activity, local, national, and global. This growing awareness and concern over crime comes at a time where, in many places in the United States, crime rates are actually falling and law enforcement is more effective than ever before in protecting citizens from criminal activity.
	At the same time, the public has been informed for several years now that crime rates are on the decline, and that in most major cities in the United States there is actually less crime now than there has been for many years1. Is this true? How does one reconcile declining crime rate statistics with one’s own experience of becoming aware of more and more crime as time goes on? One approach is to let the responsibility rest with the media: if the media reports more crime, then the public will be more and more aware of it, despite general decreases in the crime rate overall. Another approach is to acknowledge that one’s personal experience changes over the course of time, and that perhaps as one’s age increases, one’s awareness of larger societal issues also tends to grow.
	This project seeks to explore crime in one US city: Portland, Oregon. Of necessity, because of the length of this paper and the time allotted for its completion, the exploration will be an initial one, intended mainly to raise questions for further investigation. For example, there are several places in the project that the desire for more information, especially in regards to statistical investigation, is desired. While it may have been possible to calculate, for example, a simple linear regression to model a particular situation, it is not clear that a particular model would have been appropriate for a given situation. To avoid making unwarranted conclusions, or biasing one’s view of the data presented, no such models were attempted. It is hoped that the exploration below will serve as a catalyst for further investigation, rather than as an answer to every question that may arise.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
